Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-11-05 paper/paper-MinD.tex
add notes and significance Tested everything on bennet.

\significancetext{In order to determine blah de blah...}

@@

\keywords{MinD | oscillation | stochastic | deterministic | simulation}

\abbreviations{SAM, self-assembled monolayer; OTS,
octadecyltrichlorosilane}

@@

>>>>

\significancetext{When an E. Coli cell divides it must split into two
  relatively equal volumes in order to survive.  One mechanism that
  aids in this process is a system of proteins that oscillate between
  cell ends and help the original cell divide along it’s center.  A
  recent experiment found that by drastically deforming these cells
  this oscillation can be disrupted.  We examine these oscillations in
  similarly deformed cells computationally, using two widely used
  simulation models, and find good agreement using one of them.  The
  other model fails in a manner far more dramatic than has been
  previously observed.  Furthermore, we find that the effect observed
  experimentally in asymmetric and flattened cells is primarily a
  result of the flattening, not the asymmetry.  }

@@

\keywords{\fixme{E. Coli | MinD | oscillation | stochastic | deterministic | simulation}}

\abbreviations{\fixme{SAM, self-assembled monolayer; OTS,
octadecyltrichlorosilane}}

@@

\fixme{look for easily cut citations.}
